\documentclass{resume} 

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Hamzah Punjabi} 
\address{+1 (709) 725-5529 \\ 13A Wexford Street, St. John's, NL, Canada} 
\address{\href{https://hamzahap.github.io/hapunjabi/}{Website} $\diamond$
\href{mailto:hamzahqatar123@gmail.com}{Email} \\ \href{https://www.linkedin.com/in/hamzahpunjabi/}{LinkedIn} \\ \href{https://github.com/hamzahap}{Github}
}  

\begin{document}

\begin{rSection}{Education}

{\bf Memorial University of Newfoundland and Labrador} 
 \hfill {January 2019 – August 2023}\\
\normalfont Bachelor of Science in Computer Science \\
\normalfont GPA: 3.46 

\end{rSection}

\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
Languages & \normalfont Python, HTML, CSS, SQL, C\#, C, C++, Java, Fortran, PHP, JavaScript, TeX \\
Frameworks & \normalfont React.js, Laravel,  Node.js, Docker, REST, .NET, Express.js, Flask \\
Tools & \normalfont Git, MongoDB, MySQL, SQLite, Heroku, Unity, Jupyter, Visual Studio \\
AWS & \normalfont IAM, EC2, ECS, RDS, Aurora, Route 53, S3, Lambda, DynamoDB, CloudFront, VPC, Athena, \\
    & \normalfont Kinesis, ElastiCache, EKS, App Runner, SQS, CloudWatch
\end{tabular}\\
\end{rSection}

\begin{rSection}{Work History}
\vspace{-1.25em}
\item \textbf{Software Developer Intern,} {SmartICE} \hfill September 2021 - August 2022
\begin{itemize}
    \itemsep -3pt {} 
    \item \normalfont Maintained a dashboard application for SmartICE technology utilizing Laravel, ReactJS, ChartJS and Leaflet.
    \item \normalfont Integrated REST API functionality and caching into the dashboard to optimize database query performance.
    \item \normalfont Streamlined team collaboration and project management for SmartICE technology with Jira, Asana, and Github.
    \item \normalfont Managed codebase with Git for efficient version control.
    \item \normalfont Wrote Python encrypted database backup script to safeguard server data.
    \item \normalfont Programmed ADXL343 accelerometer into the SmartBUOY board in C using CCS compiler as a feature.
    \item \normalfont Developed a Windows Forms feature in C\# for SmartQAMUTIK data that enabled remote report generation, PDF conversion, Dropbox saving via Dropbox API, as well as remote viewing and sharing of SmartQAMUTIK data, resulting in improved efficiency and productivity.
    \item \normalfont Documented comprehensive work instructions for clear and accurate knowledge sharing.
 \end{itemize}
\end{rSection} 

\begin{rSection}{PROJECTS}
\\
\begin{itemize}
    \itemsep -3pt {} 
     \item \bf LaTeX Resume Tailor (Spring 2023) - \normalfont Developed a local web application using Python (Flask) for the backend and ReactJS for the frontend. The tool allows users to upload a LaTeX resume, select, rearrange, and edit specific sections, and then generate a tailored version emphasizing relevant experiences and skills for job applications.
     \item \bf Personal Website (Winter 2023) - \normalfont Developed a personal website using ReactJS and NodeJS and is hosted on Github Pages. The website showcases my skills, and includes a portfolio of my projects and achievements.
     \item \bf Wine Quality (Fall 2023) - \normalfont Conducted a data preprocessing project in Jupyter Notebook analyzing the Wine Quality Data Set from the UCI Machine Learning Repository. Conducted supervised learning, which included data analysis, feature engineering, creating missing values, and prediction of those missing values.
     \item \bf EncryptionDecryption (Winter 2022) - \normalfont Created a simple Encryption/Decryption/Backup script using PyMySQL, pandas, and Cryptography to back up database tables with CSV files.
     \item \bf Blood2D (Fall 2022) - \normalfont Developed a game using the SFML library in C++ as a group project. The game included advanced features such as collisions, inventory, game progression, shaders, custom user interface, advanced NPCs, and a custom level creation tool.
     \item \bf Canadian Pollution Visualizer (Winter 2021) - \normalfont Developed a web program using NodeJS for the backend and ReactJS for the frontend as a group project. The program enabled users to generate various types of graphs and filter data for the graphs.
\end{itemize}
\end{rSection} 
\end{document}
